Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-04 ms/main.tex
minor fixes and formatting in corolarries

\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:intermediate_association}
Cooperation will increase from rarity if social association is high enough, specifically if
  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
    \begin{aligned}
     a_2 < \alpha
    \end{aligned}
    \end{equation} 
\end{corollary}

@@

With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex
and we focus on local rather than on global stability.
To proceed,  note that 
Eq.\ \ref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
%TODO Equation 4 does not give $\hat{p}$---MWF
Eq.\ \ref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
Eq.\ \ref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
%: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.

@@

\begin{corollary}[Intermediate association of transmission and cooperation]
\label{corollary:intermediate_association_res3}
Cooperation will increase from rarity if social association is high enough, specifically if
  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
    \begin{aligned}
     \hat a_2 < \alpha.
    \end{aligned}
    \end{equation} 
\end{corollary}
\autoref{fig:result3}cd illustrates this conditions.

Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$. When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases
and therefore, a greater value of social association is required for fixation of cooperation from rarity. When $T_B>T_A$ decreasing of $v$ increases the boundary $\hat{a}_2$ 
and therefore, a greater value of social association is required for fixation of cooperation from rarity.
\\

>>>>

\begin{corollary}[Intermediate association of transmission and cooperation]\label{corollary:intermediate_association}
Cooperation will increase from rarity if social association is high enough, specifically if $a_2 < \alpha$.
\end{corollary}

@@

With both vertical and oblique transmission, $0<v<1$, the recursion system is more complex
and we focus on local rather than on global stability.
To proceed,  note that 
\autoref{eq:horizontal} gives $\hat{p}'$ as a function of both $p'$ and $\tilde{p}'$.
\autoref{eq:nextgen_adults_slimpify} gives $p'$ as a function of $\tilde{p}$, since $\hat{p}$ is given in Eq.\ \ref{eq:horizontal} as a function of $\tilde{p}$ and 
\autoref{eq:nextgen_parents_simplified} gives $\tilde{p}'$ as a function of $\hat{p}$. 
%TODO cleanup 
Combining these equations, we find an equation for $\hat{p}'$ as a function of $\hat{p}$ (shown in Appendix~\autoref{sec:appendixA}),
determine the equilibria, namely, solutions of $\hat{p}' = \hat{p}$, and analyse their local stability.
%: an equilibrium $\hat{p}^*$ is locally stable when the derivative of $f(\hat{p})=\bar{w}(\hat{p}'-\hat{p})$ at the equilibrium is negative, $f'(\hat{p}^*)<0$.

@@

\begin{corollary}[Intermediate association of transmission and cooperation]
\label{corollary:intermediate_association_res3}
Cooperation will increase from rarity if social association is high enough, specifically if $\hat a_2 < \alpha$.
\end{corollary}
\autoref{fig:result3}cd illustrates this conditions.

Note that when $T_A>T_B$ then $\partial \hat a_2 / \partial v = b T_A (T_A-T_B) > 0$, and when $T_A<T_B$ then $\partial \hat a_1 / \partial v = b(1+b-c)T_B(T_A-T_B) < 0$. When $T_A>T_B$ and the vertical transmission $v$ increases the boundary $\hat{a}_2$ also increases and therefore, a greater value of social association is required for fixation of cooperation from rarity. When $T_B>T_A$ decreasing the vertical transmission rate, $v$, increases the boundary $\hat{a}_2$. Therefore, a greater value of social association is required for fixation of cooperation from rarity.
\\
